STJ2012 analysis

### 2016-07-29 analysis/STJ2012_analysis.Rmd
rename scripts/ -> analysis/

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 4, digits = 2)
library(phyloseq); library(vegan)

>>>>

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath(".."))
knitr::opts_chunk$set(echo = TRUE)

options(scipen = 4, digits = 2)
library(phyloseq); library(vegan)
